% ================================================================================
\documentclass{article}
\pagestyle{plain}
\usepackage{fullpage}
% ================================================================================
%\usepackage[left=1in,right=1in, top=1.2in,bottom=1.2in]{geometry}
%\usepackage{times}
\usepackage{amssymb,amsthm,latexsym,amsmath,epsfig,pgf}

\usepackage{graphicx}
\usepackage{comment}
\usepackage{url}
\usepackage{hyperref}

\usepackage{blkarray}
\usepackage{tikzsymbols}
% ================================================================================
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{algorithm}

\algnewcommand\algorithmicinput{\textbf{Input:}}
\algnewcommand\Input{\item[\algorithmicinput]}

\algnewcommand\algorithmicoutput{\textbf{Output:}}
\algnewcommand\Output{\item[\algorithmicoutput]}
% ================================================================================
\newtheorem{theorem}{Theorem}[section]
\newtheorem*{theorem A}{Theorem A}
\newtheorem*{theorem B}{N\"olker's Theorem}
\newtheorem{lemma}{Lemma}[section]
\newtheorem{proposition}{Proposition}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{definition}{Definition}
\newtheorem{problem}{Problem}
\newtheorem*{question}{Question}
\newtheorem {conjecture}{Conjecture}
\theoremstyle{remark}
\newtheorem{remark}{Remark}[section]
\theoremstyle{remark}
\newtheorem{remarks}{Remarks}
% ================================================================================
\begin{document}
% ================================================================================
\title{Proposal: BlueTransience}
% ================================================================================
\author{Carolin Z\"obelein\thanks{The author believes in the importance of the independence of research and is funded by the public community. If you also believe in this values, you can find ways for supporting the author's work here: \url{https://research.carolin-zoebelein.de/funding.html}, Email: \href{mailto:contact@carolin-zoebelein.de}{\texttt{contact@carolin-zoebelein.de}}, PGP: D4A7 35E8 D47F 801F 2CF6 2BA7 927A FD3C DE47 E13B, \url{https://research.carolin-zoebelein.de}, \texttt{id: proposal\_0020}}}
% ================================================================================
\date{July 12, 2020}
% ================================================================================
\maketitle
% ================================================================================
\begin{center}
    Status: Just an idea
\end{center}
% ================================================================================
\begin{abstract}
    A Bluetooth based, short memory, social media mobile network app.
\end{abstract}
% ================================================================================
\providecommand{\keywords}[1]{\small{\textbf{\textit{Keywords:}} #1}}
\keywords{Bluetooth, Mobile App, Social Media, Natural Disaster, Political Demonstrations, Internet Shutdown}

%\providecommand{\Classification}[1]{\small{\textbf{\textit{2010 Mathematics Classification:}} #1}}
%\Classification{}
% ================================================================================
%\tableofcontents
% ================================================================================
% --------------------------------------------------------------------------------
\section{Problem statement}
\label{s:problemstatement}
% --------------------------------------------------------------------------------
In natural disaster or difficult political situations, people still need the possibility for a privacy preserving social media communication possibility for fast exchange of information.
% ================================================================================
% --------------------------------------------------------------------------------
\section{Solution concept}
\label{s:solutionconcept}
% --------------------------------------------------------------------------------
% --------------------------------------------------------------------------------
\subsection{Kind}
\label{ss:kind}
% --------------------------------------------------------------------------------
\begin{flushleft}
    \textbf{Type.}\\
    Mobile App

    \vspace{0.3cm}
    \textbf{Area.}\\
    Data security
\end{flushleft}
% --------------------------------------------------------------------------------
\subsection{Short description}
\label{ss:shortdescription}
% --------------------------------------------------------------------------------
A mobile app which establishes a Bluetooth based social media network between all participating app devices. Designed to work decentralized, mesh, organized, with focus on participant anonymization. The social media data (posts, ...) will be only saved as short term memory, like in a brain short term memory (see e.g. Snapchat) and then, not reconstructable, permanent removed.
% --------------------------------------------------------------------------------
\subsection{Aim}
\label{ss:aim}
% --------------------------------------------------------------------------------
To protect privacy, in time critical social media communnication during crises respectively sensitive political situations.
% --------------------------------------------------------------------------------
\subsection{Targets}
\label{ss:targets}
% --------------------------------------------------------------------------------
\begin{enumerate}
    \item Politicial engaged people at mass events (like e.g. political demonstrations) who needs a fast and flexible information flow of important news, but who also take care for their privacy just because of their political commmitment, at the same time.
    \item People in areas of natural disasters in which an area-wide network coverage can not be guaranteed anymore and information flow is needed.
    \item People in countries with temporary internet shutdown by government where an ongoing information flow is still necessary and the possibility to do this without fear of represssion.
\end{enumerate}
% ================================================================================
%\section*{References}
% --------------------------------------------------------------------------------
%\newpage
%\clearpage
%\markboth{Bibliography}{Bibliography}
%\section*{Bibliography}
%\label{s:bibliography}
% --------------------------------------------------------------------------------
%\bibliographystyle{amsplain}
%\bibliographystyle{unsrtdin}
%\bibliographystyle{plain}

%\nocite{*}
%\bibliographystyle{unsrtdin}
%\bibliography{proposal-bluetransience}
% ================================================================================
\section*{License}
\label{s:license}
% --------------------------------------------------------------------------------
If you like the idea and have more time like I do, feel free to take it and bring it to life. \Cooley
\begin{center}
	\url{https://creativecommons.org/licenses/by-sa/4.0/}
\end{center}
% ================================================================================
\end{document}
% ================================================================================
